An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-30 Revision/response.tex

%%%%%%%%%%%%%%%%%%%% Summary %%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{summary}[Summary Comments.]
		\textit{The paper empirically studies performance of hybrid querying methods with respect to two types of queries: attribute filtering (AF) NN search, range filtering (RF) NN search. This is a timely problem with high practical relevance. Nevertheless, several improvements would benefit the paper. We therefore recommend a revision. The main revision points are summarized below, however, we expect that the authors do their best in addressing all points raised in the individual reviews.}
	\end{summary}
}

\noindent

%%%%%%%%%%%%%%%%%%%%%% R1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Improve the readability of some figures (e.g., performance under different attribute distributions or selectivity).}
	\end{metarevision}
}

\noindent
%\textbf{Response:} We sincerely appreciate your valuable suggestions, which provide meaningful improvements to our work. Ensuring the readability of the figures is indeed crucial. We have modified both the figure and the related description in the paper to improve readability and ensure academic rigor. \textbf{(Please see Section 4.2.3, highlighted in blue in the revised manuscript.)}
%
%\textcolor{blue}{"The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations. When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts."}
%
%For performance under different attribute distributions, to illustrate how different algorithms are affected by varying attribute distributions, we added robustness indicators (Strong and Weak) in the figure. This provides more intuitive visualization of how robust each algorithm performs across different attribute distributions. As shown in Figure\ref{fig:attribute_distribution} below.
\textbf{Response:} Thank you for your valuable suggestions. We agree that the original figure had readability issues. Based on your feedback, we have carefully revised and reanalyzed the experimental sections related to “attribute distribution” and “attribute selectivity” in the paper.

@@

Moreover, previous studies (e.g., FilteredDiskANN, Milvus) also commonly use attribute selectivity as a key metric for evaluating filtering performance.

Based on these reasons, we decided to remove the attribute distribution experiments and retain only the attribute selectivity analysis. We also removed the original Figure~\ref{fig:attribute_selectivity_2}, which displayed too many algorithms in one plot and was difficult to interpret. We believe these changes improve the clarity and readability of the paper, without reducing the completeness of the evaluation.

\begin{figure*}[t]  % 或者 [b] 放到底部
	\centering
%	\includegraphics[width=\linewidth]{fig/exp_3_1_legend.pdf}
	\includegraphics[width=\linewidth]{fig/exp_3_1.pdf}
	\caption{Effect of Attribute Distribution on Query Performance (Strong indicates robustness to attribute distribution shifts, Weak indicates sensitivity)}
	\label{fig:attribute_distribution}
\end{figure*}

For performance under different attribute selectivity, to reflect the performance differences of each algorithm under varying attribute selectivities, we added performance rankings for each algorithm across different selectivity levels in the figure. This provides a clearer illustration of how each algorithm is affected by attribute selectivity rates. As shown in Figure~\ref{fig:attribute_selectivity} below.

\begin{figure*}[t]  % 可改为 [b] 放在页面底部
	\centering
%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
	\includegraphics[width=\linewidth]{fig/exp_5_2_1.pdf}
	\caption{Different Attribute Selectivity (AS) under the Same Algorithm}
	\label{fig:attribute_selectivity}
\end{figure*}

\begin{figure}[htbp]
	\centering
%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
	\includegraphics[width=\linewidth]{fig/exp_5_1_1_SingleLabel_1thread.pdf}
	\caption{Different AS under the Same Algorithm}
	\label{fig:attribute_selectivity_2}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%% R2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Run experiments with multi-modal queries (e.g., combining text and images) or more complex query types involving both attribute and range filters.}
	\end{metarevision}
}

@@

\textbf{In-memory Methods:}
FilteredVamana achieves a good balance, staying under 30 ms while achieving Recall@10 > 0.97.
While StitchedVamana achieves extremely low latency (sub-5 ms) due to its stitched multi-label index structure, its fixed edge connectivity may limit effectiveness under highly uncorrelated label distributions. Nevertheless, it consistently supports 90\%+ Recall@10 across diverse datasets, as shown in our evaluations.

\textbf{Note: }Due to space limitations and the fact that only one method supports disk-based execution, we did not include the above experiments and analysis in the revised paper.

%%%%%%%%%%%%%%%%%%%%%% R7 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Report the peak memory usage of query processing.}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons. \textbf{(Please see Section 4.2.1 and Section 4.3.1, highlighted in blue in the revised manuscript.)}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{fig/legend_only.pdf}
	\includegraphics[width=\linewidth]{fig/searchMem/label_memory_comparison.pdf}
	\caption{Attribute Filtering Search Peak Memory}
	\label{fig:search_memory_mb_comparison}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{fig/rangeFilter_legend_only.pdf}
	\includegraphics[height=2.5cm]{fig/searchMem/range_memory_comparison.pdf}
	\caption{Range Filtering Search Peak Memory}
	\label{fig:rangeFilter_search_memory_mb}
\end{figure}

@@

%For attribute filtering, please see section 4.2.1.
% \textbf{(Please refer to the blue highlighted parts in Section 4.2.1 for attribute filtering.)}
Section 4.2.1:
\textcolor{blue}{"Most algorithms load both the index and the dataset into memory during the build and query phases, and the construction process typically generates a large amount of temporary data. As a result, peak memory usage during querying is generally slightly lower than during construction. However, exceptions exist. As shown in Figure~\ref{fig:search_memory_mb_comparison}, CAPS incurs significantly higher peak memory usage during querying due to the need to dynamically maintain a large candidate set."}

%For range filtering, please see section 4.3.1.
 %\textbf{(Please refer to the blue highlighted parts in Section 4.3.1 for range filtering.)}
 Section 4.3.1:
\textcolor{blue}{"As for the search peak memory usage, we can find from the Figure ~\ref{fig:rangeFilter_search_memory_mb} that it is basically consistent with the build peak memory usage trend. As we analyzed in the section on attribute filtering."}

%%%%%%%%%%%%%%%%%%%%%% R8 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Run Scalability experiments with larger datasets.}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
Thank you for your valuable suggestion regarding our experiments. In Section 4.2.3 and Section 4.3.3, we have added experiments on the Deep100M dataset. The results show that most algorithms struggle to balance performance with time and space costs on this large-scale dataset. In particular, StitchedVamana performs poorly on Deep100M. \textbf{(Please see the "Large-scale Datasets" part of Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}
%\textbf{(Please refer to the blue highlighted parts in Section 4.2.4 and Section 4.3.4 under Large-scale Datasets.)}

@@

\end{table*}

\section*{Response to Review 1}

%%%%%%%%%%%%%%%%%%%%%% W1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{Although the authors justify the synthetic attribute generation, real-world applications may involve more complex attribute semantics and correlations, which might affect generalizability.}
	\end{weakness}
}

\noindent
\textbf{Response:} I really appreciate your suggestion. Current hybrid query algorithms do not explicitly model or leverage complex semantic relationships, such as those between vectors and their attributes, or among different attributes. However, our evaluation covered a range of realistic scenarios, including multi-attribute setting, diverse distributions and selectivity, to assess the algorithms' generalization capabilities (though we used synthetic attributes).

@@

	\caption{Comparison of Real and Synthetic Attributes}
	\label{fig:compare}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%% W2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{weakness}
		\textit{Some figures (e.g., performance under different attribute distributions or selectivity) are dense and could benefit from cleaner presentation or summarization to improve readability.}
	\end{weakness}
}

\noindent
\textbf{Response:} 
Thank you for your feedback. We have resolved this issue;For more  details,please see Meta R1 .

@@

%%%%%%%%%%%%%%%%%%%%%% W1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{observation}
		\textit{In the experimental study, datasets did not originate from the real applications for hybrid queries.
			Regarding the datasets for AF-NN search (Msong, Audio, SIFT1M, GIST1M, GloVe, Enron),
			the attributes were generated synthetically but not real.
			Regarding the datasets for RF-NN search (Deep, YT-Audio, WIT), the data point ID was used as attribute;
			however, it is not meaningful to issue range query on data point ID.
			In order to match with the introduction, the authors are recommended to
			include a real dataset from e-commerce platform with both vectors and attributes.
		}
	\end{observation}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. We fully understand your concern regarding our use of synthetic or less meaningful attributes in the hybrid query experimental setup.

To address this critical issue and enhance the real-world relevance of our evaluation, we have incorporated two new real-world datasets with their actual attributes into our attribute filtering and range filtering experiments, and we have clarified the sources of these real-world attributes. For more details, please refer to our response to Meta R3.

For attribute filtering, by incorporating the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes, we have revised the "Single-Attribute Index Construction and Single-Attribute Query" experiments and amended the manuscript accordingly. It is also worth noting that in Section 4.2.2, under the "Single-Attribute Index Construction and Single-Attribute Query" subsection, we have removed two previous datasets (Audio and GloVe) due to space constraints. The Audio dataset was removed because its smaller scale offered limited reference value. The GloVe dataset is similar in scale to SIFT1M, while LID is similar to GIST1M. \textbf{(Please see Section 4.2.1, and the "Single-Attribute Building and Single-Attribute Query" subsection in Section 4.2.2,  highlighted in blue in the revised manuscript.).}

### 2025-07-30 Revision/response.tex

Section 4.2.4: \textcolor{blue}{
	"We conducted experiments on the text2image-mix dataset. This dataset contains both image and text vectors. It is a more complex multimodal dataset. As shown in Figure 12, although the queries are more complex, UNG and NHQ still perform the best. CAPS is the next best.
	Since the dataset mixes two modalities, the ground truth of the query set usually corresponds to the same modality. The nearest neighbors in the index are often from the same modality because they are closer in distance. Therefore, the search results on this dataset are similar to those in Figure 4. UNG and NHQ perform the best. CAPS clusters based on vector similarity. It actually clusters the vectors into the same modality. Then it uses attribute filtering to divide the data further. This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
	In contrast, the text2image dataset shown in Figure 11 is different. The queries and the dataset are from different modalities. The queries are far from the dataset. The ground truths are also scattered and not clustered together. To find the ground truths, the algorithm often needs to traverse more points. This is a greater challenge for the algorithms." 
}

Section 4.3.4:\textcolor{blue}{
		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 16a is also consistent with the single-modality results in Figure 14. As shown in Figure 15, the algorithms still perform the worst on multimodal datasets like Text2Image. This is because these range query algorithms are almost graph-based. Graph algorithms need more iterations to find true neighbors in OOD datasets."
}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.95\linewidth]{fig/attribute_legend.pdf}
	\includegraphics[width=\linewidth]{fig/attribute_multimodel_2.pdf}
	\caption{Attribute Filtering Multi-modal}
	\label{fig:attribute_multimodel}
\end{figure}

### 2025-07-30 Revision/response.tex

	\caption{Different Attribute Selectivity (AS) under the Same Algorithm}
	\label{fig:attribute_selectivity}
\end{figure*}
\begin{figure}[htbp]
	\centering
	%	\includegraphics[width=0.8\linewidth]{fig/exp_5_2_1_legend.pdf}
	\includegraphics[width=\linewidth]{fig/exp_5_1_1_SingleLabel_1thread.pdf}
	\caption{Different AS under the Same Algorithm}
	\label{fig:attribute_selectivity_2}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%% R2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Run experiments with multi-modal queries (e.g., combining text and images) or more complex query types involving both attribute and range filters.}
	\end{metarevision}
}

\noindent
\textbf{Response:} We believe this is an excellent suggestion. To provide a more comprehensive evaluation of the robustness of each algorithm, we introduce new experiments on two challenging multi-modal datasets.

First, we have incorporated a standard text-to-image dataset, which is widely adopted by existing multi-modal ANN algorithms. In this dataset, the base vectors are images while the query set consists of texts, creating a modality gap that demands stronger algorithm robustness to achieve good performance. Second, to further test performance on complex queries, we have constructed a more challenging dataset with a base set of 500,000 text vectors and 500,000 image vectors, and a query set containing 5,000 text and 5,000 image vectors. On this latter dataset, we perform both attribute filtering and range queries using combined text and image inputs to analyze the algorithm's robustness under more complex, mixed-modality conditions. The experimental results are shown in Figure~\ref{fig:attribute_multimodel} and Figure~\ref{fig:range_multimodel}.

As for complex query types that involve both attribute filtering and range queries simultaneously, to the best of our knowledge, existing algorithms—except for general-purpose systems such as Milvus and Faiss—do not support this functionality. For example, ACORN needs to build separate indexes for each scenario and cannot handle attribute filtering and range queries simultaneously. Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately. \textbf{(Please see Section 4.1.1, Section 4.2.3 and Secntion 4.3.3, highlighted in blue in the revised manuscript.)  
	%Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
}

@@

Section 4.1.1:\textcolor{blue}{
"Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms. The Text2Image dataset includes two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings."
}

Section 4.2.3: \textcolor{blue}{
	"We conducted experiments on the text2image-mix dataset. This dataset contains both image and text vectors. It is a more complex multimodal dataset. As shown in Figure 12, although the queries are more complex, UNG and NHQ still perform the best. CAPS is the next best.
	Since the dataset mixes two modalities, the ground truth of the query set usually corresponds to the same modality. The nearest neighbors in the index are often from the same modality because they are closer in distance. Therefore, the search results on this dataset are similar to those in Figure 4. UNG and NHQ perform the best. CAPS clusters based on vector similarity. It actually clusters the vectors into the same modality. Then it uses attribute filtering to divide the data further. This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
	In contrast, the text2image dataset shown in Figure 11 is different. The queries and the dataset are from different modalities. The queries are far from the dataset. The ground truths are also scattered and not clustered together. To find the ground truths, the algorithm often needs to traverse more points. This is a greater challenge for the algorithms." 
}

Section 4.3.3:\textcolor{blue}{
		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 16a is also consistent with the single-modality results in Figure 14. As shown in Figure 15, the algorithms still perform the worst on multimodal datasets like Text2Image. This is because these range query algorithms are almost graph-based. Graph algorithms need more iterations to find true neighbors in OOD datasets."
}

@@

\textbf{Regarding the experimental parameter settings:}

For datasets with recommended parameters provided in the original papers, we directly used those recommended settings. For other datasets, we selected the parameter combinations that performed best through empirical evaluation. All parameters used in the experiments are available in our public code repository.

According to our experimental results, for datasets using the recommended parameters, the algorithm rankings remained unchanged. During the search process, we adjusted the search parameters to obtain different Recall and QPS values. The search parameters typically span a wide range of values to ensure the completeness of the experimental results.

Due to the large number of algorithms and datasets involved, we did not include all parameter settings in the paper because of space limitations. The detailed parameter configurations can be found in our public code repository. (\textbf{Please see Section 4.1.3, highlighted in blue in the revised manuscript.})

	\textcolor{blue}{
%"In the experiments, for datasets with recommended parameters in the original paper, we use the recommended settings. For datasets without recommended parameters, we conduct experiments with different parameter settings and select the one that performs best for the final experiment.Due to the large number of datasets and algorithms involved, the parameters are not listed individually, but they are provided in the code repository."}
Regarding experimental parameter selection, we adopted the recommended settings from original papers when available. For datasets without suggested parameters, we experimented with different configurations and selected the optimal one for final evaluation. Due to the extensive number of datasets and algorithms involved, specific parameters are not listed individually but are provided in our code repository.}

@@

Regarding the issue of range attributes, we indeed used only one range attribute for evaluation. At present, most existing range filtering algorithms only support filtering on a single attribute. This is a major limitation of current range filtering methods. We have clearly pointed this out in Section 5.2.2 of the "Discussion" part of the paper and listed it as an important challenge for future work. Thank you for highlighting this point, which further emphasizes the significance of our work. \textbf{(Please see the "Build peak memory" part of Section 5.2.2, highlighted in green in the revised manuscript.)}

To make the paper more readable, we have added a more detailed explanation of the range attribute in Section 4.3. \textbf{(Please see Section 4.3, highlighted in blue in the revised manuscript.)}

\textcolor{blue}{"Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value. The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones. "}

In response to the large difference in index construction time shown in Figure 12a (now 13a), we have revised the paper based on your suggestion. We added more detailed and in-depth analysis to provide a clearer explanation. \textbf{(Please see the "Index construction time" part of Section 4.3.1, highlighted in blue in the revised manuscript.)}

### 2025-07-30 Revision/response.tex

\textcolor{blue}{
	"WIT-Real and YT-Audio-Real datasets use real attributes: For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description as real attributes. The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset."
}
%%%%%%%%%%%%%%%%%%%%%% R5 %%%%%%%%%%%%%%%%%%%%%%

\myfbox{
	\begin{metarevision}
		\textit{Evaluate if the server setting affects the relative ordering of methods in experiments}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
That is a great suggestion. In order to figure out if the server setting affects the relative ordering of methods, we conducted additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset.
The results show that the performance differences across algorithms remain small, and their relative rankings do not change significantly across servers.
We did observe slightly lower QPS on this server compared to our original one, which is mainly due to the the lower CPU frequency, reduced RAM capacity, and smaller L3 cache of the Xeon 6330 processors. \textbf{(Please see Section 4.2.3 and Section 4.3.3, highlighted in blue in the revised manuscript.)}

Section 4.2.3:
%\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure 12b. Compared with the experimental results on the original server, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity, the QPS values are slightly lower across all methods."}
\textcolor{blue}{"To investigate the impact of different server configurations on the performance of the algorithms, we conduct additional experiments on an Ubuntu 20.04 server equipped with dual Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz featuring 128GB of RAM and 84 MiB of L3 cache using the YT-Audio-Real dataset, and the results are shown in Figure 9b. It is not difficult to see that the relative ranking of the algorithms under the two servers essentially remains unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency, reduced RAM capacity, and smaller L3 cache, all methods demonstrate slightly lower QPS values."}

Section 4.3.3:
%\textcolor{blue}{"Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 16b. When compared with the experimental results of the original server, our findings remain consistent with those reported in Section 4.2.4. For brevity and due to space limitations, we omit further discussion of these redundant results."}
\textcolor{blue}{"Consistent with Section 4.2.3, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure 12b. Our findings remain consistent with those reported in Section 4.2.3. For brevity and due to space limitations, we omit further discussion of these redundant results."}

### 2025-07-30 VLDB2026/main.tex
Update main.tex

	(2) \textbf{Strengthening Datasets and Experimental Settings for Fair Evaluation.}
%		To ensure fair and reproducible evaluation, we generate attribute values based on real-world scenarios to enhance commonly used datasets. In addition to commonly used datasets, we also conduct experiments on a real-attribute dataset and a large-scale dataset (up to 100M records). Our benchmark design covers diverse selectivity levels and query conditions, establishing a unified and practical evaluation framework for hybrid query algorithms.}
%	To address the lack of standardized benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets. We also collect real attribute information from existing datasets and conduct experiments on a real attribute dataset to validate the plausibility of the generated attributes and the effectiveness of the results. To comprehensively reflect diverse real-world application needs, we design experiments covering varying attribute distributions, selectivity levels, and query conditions, ensuring representative and practical evaluation. \textcolor{cyan}{Furthermore, we test on a large-scale dataset containing 100 million records and a multi-modal dataset to analyze the scalability and performance of various algorithms.} These enhancements establish a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
	To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios. We design comprehensive experimental settings that reflect diverse application requirements, \textcolor{violet}{including varying selectivity, number of attributes participating in index construction, and number of query attributes.} \textcolor{cyan}{Furthermore, to investigate the scalability and adaptability of the algorithms, we conduct extended experiments on a large-scale dataset and 2 multi-modal datasets.} These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.

@@

%	(3){ Evaluation of Attribute and Range Filtering Algorithms.}
%	\textcolor{cyan}{We conduct a comprehensive and integrated evaluation of 7 attribute filtering algorithms, 5 range filtering algorithms, 1 vector library, and 3 databases. We compare the index construction and query performance of each method across different scenarios using 5 core metrics. We identify the reasons for performance differences based on the design of the algorithms and summarize their respective strengths and weaknesses.}
	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets. By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method. We further examine their behavior under different attribute selectivity to assess robustness and adaptability in complex query scenarios. Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.
%	\textcolor{orange}{We conduct a comprehensive evaluation of 6 attribute filtering algorithms, 1 library, and 3 databases across 6 basic datasets, 2 real-world datasets, one 100M-scale dataset, and 2 multimodal datasets. By analyzing the query performance of each method under various scenarios, we reveal their respective strengths and weaknesses. We further examine their robustness by evaluating performance under different attribute distributions and selectivity levels. To ensure fairness and generality, we evaluate the methods on two different server environments. The evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.}
%

	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments. The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance. We further analyze the factors that affect the performance of the range filtering algorithms.
%	\textcolor{orange}{
%		We conduct benchmark evaluations of range filtering algorithms on one synthetic and 2 real-world datasets, using various query range settings. Our experiments reveal and analyze the differences in time and query efficiency across these algorithms. Furthermore, we compare their performance on multimodal and large-scale datasets, and assess their adaptability across different server environments.
%	}

@@

	{(5)\textbf{ Recommendations and Challenges.}
%	Based on the experimental results, we provide a recommendation table that shows the performance of each algorithm in different scenarios. Readers can select suitable algorithms according to their specific application needs. In addition, we identify key challenges in the field of hybrid queries. These challenges include the lack of consideration for the correlation between attributes and vectors, limited support for Boolean logic, insufficient capability for multi-attribute range filtering, and sensitivity of algorithms to data distribution. Currently, few methods support both attribute filtering and range filtering at the same time. This indicates potential directions for future research.
%%}
	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries. These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution. Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.

@@

	\textcolor{violet}{Our experiments employ 12 real-world datasets covering diverse domains: Audio~\cite{audio_unknown}, Deep1M~\cite{yandex_deep_dataset}, Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}

	\textcolor{violet}{The first seven datasets are widely used in existing works. As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution.}

	\textcolor{violet}{WIT-Real and YT-Audio-Real datasets use real attributes. For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description  as real attributes. The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset.}

@@

				%YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
				Deep1M & 96 & 1,000,000 & 10,000 & 22 & Image& RF \\
				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio& Both \\
				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image& Both \\
				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image& Both \\
				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image& Both \\
				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image& Both \\
				\bottomrule
			\end{tabular}
		}
	\end{table}

>>>>

	(2) \textbf{Strengthening Datasets and Experimental Settings for Fair Evaluation.}
%		To ensure fair and reproducible evaluation, we generate attribute values based on real-world scenarios to enhance commonly used datasets. In addition to commonly used datasets, we also conduct experiments on a real-attribute dataset and a large-scale dataset (up to 100M records). Our benchmark design covers diverse selectivity levels and query conditions, establishing a unified and practical evaluation framework for hybrid query algorithms.}
%	To address the lack of standardized benchmarks in attribute filtering research, we generate attribute values based on real-world scenarios to enhance commonly used datasets. We also collect real attribute information from existing datasets and conduct experiments on a real attribute dataset to validate the plausibility of the generated attributes and the effectiveness of the results. To comprehensively reflect diverse real-world application needs, we design experiments covering varying attribute distributions, selectivity levels, and query conditions, ensuring representative and practical evaluation. \textcolor{cyan}{Furthermore, we test on a large-scale dataset containing 100 million records and a multi-modal dataset to analyze the scalability and performance of various algorithms.} These enhancements establish a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.
	To address the lack of standardized benchmarks in attribute filtering research, we enrich commonly used datasets by generating attribute values tailored to real-world scenarios. We design comprehensive experimental settings that reflect diverse application requirements, \textcolor{violet}{including varying vector datasets, number of attributes participating in index construction, number of query attributes, and selectivity. Furthermore, to further investigate the scalability and adaptability of the algorithms, we also conduct experiments on a large-scale dataset and 2 multi-modal datasets.}  These enhancements provide a unified evaluation framework that supports fair, consistent, and reproducible comparisons across different algorithms, laying a solid foundation for future research in hybrid query.

@@

%	(3){ Evaluation of Attribute and Range Filtering Algorithms.}
%	\textcolor{cyan}{We conduct a comprehensive and integrated evaluation of 7 attribute filtering algorithms, 5 range filtering algorithms, 1 vector library, and 3 databases. We compare the index construction and query performance of each method across different scenarios using 5 core metrics. We identify the reasons for performance differences based on the design of the algorithms and summarize their respective strengths and weaknesses.}
	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 9 real-world datasets. By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method. We further examine their behavior under different attribute selectivity to assess robustness and adaptability in complex query scenarios. Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.
%	\textcolor{orange}{We conduct a comprehensive evaluation of 6 attribute filtering algorithms, 1 library, and 3 databases across 6 basic datasets, 2 real-world datasets, one 100M-scale dataset, and 2 multimodal datasets. By analyzing the query performance of each method under various scenarios, we reveal their respective strengths and weaknesses. We further examine their robustness by evaluating performance under different attribute distributions and selectivity levels. To ensure fairness and generality, we evaluate the methods on two different server environments. The evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.}
%

	(4)\textbf{ Evaluation of Range Filtering Algorithms.}
	We benchmark algorithms that support range filtering on 5 real-world datasets, using varying query range settings in the experiments. The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance. we also further analyze the factors that affect the performance of the range filtering algorithms.
%	We benchmark algorithms that support range filtering on 3 large-scale datasets, using varying query range settings in the experiments. The experimental results show the performance of these algorithms in terms of index construction efficiency, storage overhead, and query performance. We further analyze the factors that affect the performance of the range filtering algorithms.
%	\textcolor{orange}{
%		We conduct benchmark evaluations of range filtering algorithms on one synthetic and 2 real-world datasets, using various query range settings. Our experiments reveal and analyze the differences in time and query efficiency across these algorithms. Furthermore, we compare their performance on multimodal and large-scale datasets, and assess their adaptability across different server environments.
%	}

@@

	{(5)\textbf{ Recommendations and Challenges.}
%	Based on the experimental results, we provide a recommendation table that shows the performance of each algorithm in different scenarios. Readers can select suitable algorithms according to their specific application needs. In addition, we identify key challenges in the field of hybrid queries. These challenges include the lack of consideration for the correlation between attributes and vectors, limited support for Boolean logic, insufficient capability for multi-attribute range filtering, and sensitivity of algorithms to data distribution. Currently, few methods support both attribute filtering and range filtering at the same time. This indicates potential directions for future research.
%%}
	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid query. These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to selectivity. Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.

@@

	\textcolor{violet}{Our experiments employ 12 real-world datasets covering diverse domains: Audio~\cite{audio_unknown},  Enron~\cite{enron2015}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Msong~\cite{msong2011}, SIFT1M~\cite{sift2010}, Deep1M~\cite{yandex_deep_dataset}, WIT-Real~\cite{wit_dataset}, YT-Audio-Real~\cite{youtube8m_dataset}, Text2image~\cite{texttoimage}, Text2image-Mix, and Deep100M.}

	\textcolor{violet}{The first seven datasets are widely used in existing works. As they do not inherently come with attributes, we generate attributes for them to precisely control attribute quantity and distribution. WIT-Real and YT-Audio-Real datasets use real attributes. For the WIT-Real dataset, we use the CLIP model to encode the page title into vectors, and extract the language type and the length of the context page description  as real attributes. The YT-Audio-Real dataset uses YouTube8M data, employing the video category ID and view counts as real attributes for this dataset.}

@@

				%YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
				Deep1M & 96 & 1,000,000 & 10,000 & 22 & Image& RF \\
				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image& Both \\
				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio& Both \\
				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image& Both \\
				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image& Both \\
				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image& Both \\
				\bottomrule
			\end{tabular}
		}
	\end{table}
